### 2013-10-16 chi2014/qualitative.tex
2/8 mike feedback

To complete the brainstorming task, participants had to generate some number of uses for a partially broken MP3 player. Under the problem scoping strategy, this problem can reduced in scope to one of many sub-problems: brainstorm uses for \emph{an audio output device}; brainstorm uses for \emph{an electronic screen}; brainstorm uses for \emph{a hard drive}; and so on. The participant chooses one sub-problem at a time and generates solutions, each of which is also a solution to the original problem. For example, the following are generated by PXXX focusing on the audio output capabilities of an MP3 player:

@@

The previous examples of problem scoping are examples of emphasizing specific details of the problem. Problem scoping can also entail neglecting details. For example, the following ideas from PXXX apply to almost any physical object, not just the MP3 player described:

@@

We refer to the former, detail-oriented kind of problem scoping as \emph{scoping inward} and the alternative as \emph{scoping outward}. These two types of scoping cover almost all responses. However, some responses employ no scoping whatsoever. These responses utilize the device exactly as it was intended, as a portable MP3 player. For example, "get it fixed and give it to a needy kid".

Problem scoping is employed by all participants, but the type of scoping is a useful discriminant.

>>>>

Under the problem scoping strategy, the original problem is transformed to a new problem of reduced scope.
An MP3 player has many functions which are difficult to leverage simultaneously. Thus, many transformations are possible, for example: brainstorm uses for \emph{an audio output device}; brainstorm uses for a small box-shaped object; brainstorm uses for \emph{a hard drive}; and so on. The participant chooses a problem transformation and generates solutions, each of which is also a solution to the original problem. For example (PXXX):

@@

The participant's responses satisfy the transformed question "brainstorming uses for an audio output device". The resulting ideas no not rely on or acknowledge other aspects of the problem, such as portability, the screen, the ability to store files, or the appearance or size of the device. Nonetheless, each response is also a valid response to the original problem.

We distinguish between kinds of problem scoping. \emph{Inward scoping} transformations reduce scope by limiting consideration to a single detail of the problem. The previous responses, which focus on audio output, are an example of inward scoping.

\emph{Outward scoping} transformations reduce complexity by stripping all meaningful details. In the case of the MP3 player problem, this can be understood as essentially reducing the problem to "brainstorm uses for a thing". For example (PXXX):

@@

The inward scoping solutions were applicable to the transformed problem and the original problem, but not many others. In contrast, the outward scoping solutions could be applied to a wide body of problems unrelated to the original, such as "brainstorm uses for a broom". Thus, a useful rule for distinguishing the types of scoping is to consider whether the \emph{set of problems solved by the solutions} is small, or large.

These two types of scoping cover almost all responses. However, some responses employ no scoping whatsoever. These responses utilize the device exactly as it was intended, as a portable MP3 player. For example, "get it fixed and give it to a needy kid".
